Working title: Ecological network control

### 2018-05-09 paper/manuscript.Rmd
Add structural controllability figure in manuscript

>>>>

```{r, fig.cap="Consider the ", fig.height= 1.5, fig.width=3.5}
drake::loadd(en_structural)

# wether to save it as a pdf (for testing purposes)
out_pdf <- F

# format networks for plotting
formated_en_structural <- en_structural %>%
  purrr::map(~ fancify_vertex_name(.)) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "color", "type == 'a' ~ 'black'", "TRUE ~ 'azure4'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "type == 'a' ~ 'white'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "type == 'a' ~ 'black'", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "shape", "type == 'a' ~ 'circle'", "TRUE ~ 'square'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "type == 'a' ~ 55", "TRUE ~ 25")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))

if(out_pdf) pdf("test.pdf", width = 3.5, height = 1.5, paper='special')

# make graphics device layout one row on top for headings, one column on the
# left for headings and one in the middle for separator line
layout(matrix(c(8,1,7,2,
                9,3,7,4,
                10,5,7,6), nrow = 3, ncol = 4, byrow = TRUE),
       heights= c(0.25, 1, 1), 
       widths = c(0.2, 1, 0.05, 1))
par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)

# 1
plot.new()
text(0.5,0.25, "not controllable", adj = c(0.5,0), font = 2, cex = 0.9)

# 2
plot.new()
text(0.5,0.25, "controllable", adj = c(0.5,0), font = 2, cex = 0.9)

# 3-6
for (i in 2:length(formated_en_structural)){
  set.seed(5)
  types <- igraph::V(formated_en_structural[[i]])$type ==
    dplyr::first(igraph::V(formated_en_structural[[i]])$type)
  l <- igraph::layout_as_bipartite(formated_en_structural[[i]], types) %>%
    rescale_layout(xlim = c(-1.75, 1.75), ylim = c(-0.6, 0.6))
  plot_examples(formated_en_structural[[i]], 
                vertex.size = 45,
                layout = l,
                frame = F, 
                rescale = F, 
                margin = rep(0, 4))
}

# 7
plot.new()
segments(0,0,0,1, lty = 2, lwd = 0.5)
# 8
plot.new()
# 9
plot.new()
text(0.5,0.5, "inaccessible\nnode", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)
# 10
plot.new()
text(0.5,0.5, "dilation", adj = c(0.5,0.5), font = 1, cex = 0.9, srt = 90)

if(out_pdf) dev.off()

```
